---
title: "Influencer Campaign Metrics: Velocity & Adoption Analysis"
author: "Influencer CV System"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: flatly
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(data.table)
library(ggplot2)
library(dplyr)
library(tidyr)

# Source the main analysis file as a sub-process to generate the latest metrics
source('analysis.R', local = TRUE)

# Filter for videos that have hit the 48-hour maturity mark
# We use max launch_age per video to check if the video has lived long enough
videos_48h <- d[, .(max_age = max(launch_age)), by = video_id][max_age >= 48, video_id]

# Filter main dataset to only include those videos 
# and keep one definitive record per video (the peak values)
filtered_data <- d[video_id %in% videos_48h]

# Aggregate to channel level to show form
channel_summary <- filtered_data[, .(
  avg_peak_velocity = mean(peak_velocity, na.rm = TRUE),
  avg_bass_p = mean(bass_p, na.rm = TRUE),
  avg_bass_q = mean(bass_q, na.rm = TRUE),
  avg_engagement = mean(engagement, na.rm = TRUE),
  videos_tracked = uniqueN(video_id)
), by = channel_id]

```

## Overview

This report tracks the performance dynamics of influencers active in the current tracking window. The dataset is filtered to only include videos that have been actively tracked for **at least 48 hours**.

The report focuses on:
1. **Initial Hype** (Peak View Velocity)
2. **Audience Adoption Profiles** (Bass Diffusion $p$ and $q$)
3. **Intent & Quality** (Weighted Engagement Ratio)

---

## 1. Peak Velocity ($V_{max}$) 

**What this measures:** View Velocity measures the raw "Hype" and FOMO generated by the creator. It indicates how many viewers have notifications turned on and watch immediately (Views Per Hour).

```{r velocity_chart, fig.width=10, fig.height=6}
ggplot(channel_summary, aes(x = reorder(channel_id, avg_peak_velocity), y = avg_peak_velocity, fill = avg_peak_velocity)) +
  geom_col() +
  coord_flip() +
  scale_fill_viridis_c(option = "plasma", end = 0.9) +
  theme_minimal() +
  labs(
    title = "Average Peak Velocity (VPH) by Channel",
    subtitle = "Higher values indicate a stronger 'Flash' impact during launch.",
    x = "Channel ID",
    y = "Average Peak Views Per Hour",
    fill = "Velocity"
  )
```

---

## 2. Adoption Profiles (Loyalists vs. Viral Engines)

**What this measures:** We map the Bass Diffusion metrics to determine how the influencer's audience grows:
*   **Coefficient of Innovation ($p$)**: Driven by dedicated followers ("The Loyalists").
*   **Coefficient of Imitation ($q$)**: Driven by the YouTube Algorithm and social sharing ("Viral Engines").

```{r bass_scatter, fig.width=10, fig.height=6}
ggplot(channel_summary, aes(x = avg_bass_p, y = avg_bass_q, size = avg_peak_velocity, color = channel_id)) +
  geom_point(alpha = 0.8) +
  scale_size(range = c(5, 15)) +
  theme_minimal() +
  labs(
    title = "Influencer Adoption Profiles",
    subtitle = "Size of bubble indicates Peak View Velocity",
    x = "Innovation Coefficient (p) - Core Following",
    y = "Imitation Coefficient (q) - Algorithmic Virality",
    color = "Channel ID",
    size = "Peak Velocity"
  ) +
  theme(legend.position = "right")
```

---

## 3. Weighted Engagement & Intent

**What this measures:** A ratio consisting of (Likes + 2x Comments) / Views. High engagement strongly correlates with viewer satisfaction, intent to purchase, and higher Click-Through Rates (CTR).

```{r engagement_box, fig.width=10, fig.height=6}
# We use the filtered_data here to show distribution across videos per channel
ggplot(filtered_data, aes(x = reorder(channel_id, engagement, FUN = median, na.rm=TRUE), y = engagement, fill = channel_id)) +
  geom_boxplot(alpha = 0.7, outlier.shape = NA) +
  geom_jitter(width = 0.2, alpha = 0.5, size = 1) +
  coord_flip() +
  theme_minimal() +
  labs(
    title = "Engagement Distribution by Channel",
    subtitle = "Data points represent individual videos",
    x = "Channel ID",
    y = "Weighted Engagement Ratio (%)"
  ) +
  theme(legend.position = "none")

```
